Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-21 paper.qmd
Added link plots intro
Start writing about link plots

It’s important to access the \gD{} layout and the generated model overlaid on data in \pD{} together to understand whether it fits the points everywhere, fits better in some places, or simply mismatches the pattern. Interactivity also helps in understanding the quirks that occur with different NLDR techniques (XXXXRefer the video after finalising the two C-shaped clusters data).

@@

>>>>

@@

It’s important to access the \gD{} layout and the generated model overlaid on data in \pD{} together to understand whether it fits the points everywhere, fits better in some places, or simply mismatches the pattern. Interactivity also helps in understanding the quirks.

The embedding and tour views are linked together via rectangular brushes; when a brush is active, points will be highlighted in the adjacent view. Because the tour is dynamic, brush events that become active will pause the animation, so that a user can interrogate the current view.  By default, brushing on the embedding view will produce a one-to-one linking with the tour view. For interpreting specific combinations of clusters, the multiple guides on the legend can be selected in order to see their relative orientations.

The interface is constructed as a **shinygadget** specifically designed for interactive data analysis.
